Tabular Constraint Learning

### 2016-04-15 Paper/ECAI/tabular.tex
moved from formalization to statement section

\paragraph{Example}
  For example, the \template \textit{rank} has
\begin{itemize}
\item \CName: \textit{$v_r$ = RANK($v_x$)}, where $v_x$ and $v_r$ are its variables;
\item \CSignature: groups assigned to $v_x$ must be numeric, groups assigned to $v_y$ must be integer and the length of vectors in $v_x$ is the same as in $v_y$;
\item \CFunction: the mapping $\{ v_x \mapsto g_x, v_y \mapsto g_y \}$ is a solution iff $g_x \in G_x, g_y \in G_y$ ($G_x \in \groups, G_y \in \groups$) and each value in $g_y$ is the rank of the corresponding value in $g_x$ (possibly with ties).
\end{itemize}

\samuel{Should this section maybe be moved to problem statement?}
We can now define a classical constraint satisfaction problem on tables.
A {\em constraint satisfaction problem} (CSP)  consists of 1) a set of cells, and 2) a set of constraints over those cells.
Notice that the constraints specify the types (or the domains) that one encounters in traditional CSPs.
Notice also, that as in traditional CSPs, the CSP problem defines the variables (the cells) of the problem as well as the constraint that should hold amongst them. The task of CSP-solvers is then to find an assignment to the variables that satisfies all the constraints.
The distinction between variables (cells) and their assignments (their values) is important here.
So, when we speak about cells, vectors and groups, we refer to the variables; when we talk about values, assignments or instances, we refer to the values these cells take in a particular "instantiated" table.

@@

Let us introduce \template instantiation syntax. Let $S$ be a mapping from variables to the subgroups of \groups and $T$ be a \template, then $T^S$ is the template, in which all variables in all constrainst in \CSignature and \CFunction are instantiated with the corresponding subgroups from $S$. We refer to $T^S$ as a \textit{constraint} and to the instantiated \CSignature (\CFunction) as $\text{\CSignature}^S$ ($\text{\CFunction}^S$). Throughout the work we refer as \textit{find constraints} to finding all constraints that hold.

Let us now define what it means for a constraint from \template to hold in general. Let $T$ be a \template, $S$ be a mapping from variables to the subgroups of \groups, and $C$ be the constraint $T^S$, then $C$ \textit{holds} iff all constraints in $\text{\CSignature}^S$ and $\text{\CFunction}^S$ of $C$ hold.

\section{Problem Statement}
\sergey{should reflect all the changes, Luc wants to introduce constraint satisfaction into problem statement, maybe we should move the definition of a solution here? Like a solution is actually constraint satisfaction?}
In the previous section we introduced the problem of tabular constraint learning informally using the example in Figure \ref{fig:main_example}. Here we formalize the statement in terms of \template and group assignments as follows:

>>>>

\paragraph{Example}
  For example, the \template \textit{rank} has
\begin{itemize}
\item \CName: \textit{$v_r$ = RANK($v_x$)}, where $v_x$ and $v_r$ are its variables;
\item \CSignature: groups assigned to $v_x$ must be numeric, groups assigned to $v_y$ must be integer and the length of vectors in $v_x$ is the same as in $v_y$;
\item \CFunction: the mapping $\{ v_x \mapsto g_x, v_y \mapsto g_y \}$ satisfies the constraint iff $g_x \in G_x, g_y \in G_y$ ($G_x \in \groups, G_y \in \groups$) and each value in $g_y$ is the rank of the corresponding value in $g_x$ (possibly with ties).
\end{itemize}

\section{Problem Statement}
\sergey{moved from the formalization BEGIN}
We can now define a classical constraint satisfaction problem on tables.
A {\em constraint satisfaction problem} (CSP)  consists of 1) a set of cells, and 2) a set of constraints over those cells.
Notice that the constraints specify the types (or the domains) that one encounters in traditional CSPs.
Notice also, that as in traditional CSPs, the CSP problem defines the variables (the cells) of the problem as well as the constraint that should hold amongst them. The task of CSP-solvers is then to find an assignment to the variables that satisfies all the constraints.
The distinction between variables (cells) and their assignments (their values) is important here.
So, when we speak about cells, vectors and groups, we refer to the variables; when we talk about values, assignments or instances, we refer to the values these cells take in a particular "instantiated" table.

@@

Let us introduce \template instantiation syntax. Let $S$ be a mapping from variables to the subgroups of \groups and $t$ be a \template, then $t^S$ is the template, in which all variables in all constrainst in \CSignature and \CFunction are instantiated with the corresponding subgroups from $S$. We refer to $t^S$ as a \textit{constraint} and to the instantiated \CSignature (\CFunction) as $\text{\CSignature}^S$ ($\text{\CFunction}^S$). Throughout the work we refer as \textit{find constraints} to finding all constraints that hold.

Let us now define what it means for a constraint from \template to hold in general. Let $t$ be a \template, $S$ be a mapping from variables to the subgroups of \groups, and $C$ be the constraint $t^S$, then $C$ \textit{holds} iff all constraints in $\text{\CSignature}^S$ and $\text{\CFunction}^S$ of $C$ hold.
\sergey{moved from formalization END}

In the previous section we introduced the problem of tabular constraint learning informally using the example in Figure \ref{fig:main_example}. Here we formalize the statement in terms of \template and group assignments as follows:
